\begin{enumerate}[label=\thesubsection.\arabic*, ref=\thesubsection.\theenumi]
\item A batsman scored the following number of runs in 6 innings.  
	$$36, 35, 50, 46, 60, 55$$
	Calculate the mean runs scored by him in an inning.
	\\
	\solution
	\lstinputlisting{codes/data/avg.c}
\item The ages in years of 10 teachers of a school are
	$$32, 41, 28, 54, 35, 26, 23, 33, 38, 40$$
	\begin{enumerate}
		\item What is the age of the oldest teacher and that of the youngest teacher?
			\\
			\solution
	\lstinputlisting{codes/data/minmax.c}
		\item What is the range of the ages of the teachers?
		\item What is the mean age of these teachers?
	\end{enumerate}
\item Organize the following marks in a class assessment, in tabular form with columns as marks and frequency.
	\begin{gather}
	4, 6, 7, 5, 3, 5, 4, 5, 2, 6, 2, 5, 1, 9, 6, 5, 8, 4, 6, 7
	\end{gather}
	\begin{enumerate}
		\item Which number is the highest?
		\item Which number is the lowest?
		\item What is the range of the data?
		\item Find the arithmetic mean.
	\end{enumerate}
	\solution
	\lstinputlisting{codes/data/markfreq.c}
	\item 
Find the median of
		the group of 17 students with the following heights (in cm)
\begin{gather*}
106, 110, 123, 125, 117, 120, 112, 115, 
\\
110, 120, 115, 102, 115, 115, 109, 115, 101
\end{gather*}
	\\
	\solution
\lstinputlisting{codes/data/find-median.c}
\item	Sale of English and Hindi books in the years 1995, 1996, 1997 and 1998 are given below in
  \tabref{tab:sale}.  
	\begin{table}[H]
  \centering
  \input{tables/sale.tex}
  \caption{}
  \label{tab:sale}
\end{table}
Draw a double bar graph and answer the following questions
\begin{enumerate}
\item In which year was the difference in the sale of the two language books least?.
\item  Can you say that the demand for English books rose faster? Justify.
\end{enumerate}
	\solution
	\lstinputlisting{codes/data/bar.c}
\item Following are the margins of victory in the football matches of a league.  Find the mode of this data.
	\begin{gather*}
	1,3,2,5,1,4,6,2,5,2,2,2,4,1,2,3,1,1,2,3,2,6,4,3,2,
	\\
	1,1,4,2,1,5,3,3,2,3,2,4,2,1,2.
	\end{gather*}
	\solution
\lstinputlisting{codes/data/findmode.c}
\end{enumerate}
